### 2020-05-24 writeup/proof_technical.tex
re-structure

>>>>

\begin{theorem}\label{thm_many_tasks}
	Let $n = c \cdot p$.
	Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
	Let $U_r U_r^{\top}$ denote the best rank-$r$ approximation subspace of $B^{\star}\Sigma B^{\star}$, where $U_r\in\real^{k\times r}$.
	Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
	We have the following
	\begin{itemize}
		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} \ge \norm{\Sigma (B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} < \norm{\Sigma(B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{theorem}
As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$, for any $1 \le i \le k$. Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\beta}$. The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.

### 2020-05-24 writeup/transfer.tex
re-structure

@@

\begin{theorem}\label{thm_many_tasks}
	Let $n = c \cdot p$.
	Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
	Let $U_r U_r^{\top}$ denote the best rank-$r$ approximation subspace of $B^{\star}\Sigma B^{\star}$, where $U_r\in\real^{k\times r}$.
	Let $U_r(i)$ denote the $i$-th row vector of $U_r$.
	We have the following
	\begin{itemize}
		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} \ge \norm{\Sigma (B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If $(1 - \norm{U_r(i)}^2)\cdot \frac{\sigma^2}{c - 1} < \norm{\Sigma(B^{\star} U_r U_r(i) - \beta_i)}^2$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{theorem}
As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$, for any $1 \le i \le k$. Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\beta}$. The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.

>>>>

We assume that for every row $x^\top$ of $X_i$, we have $\ex{xx^{\top}} = \Sigma_i.$
We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector that has i.i.d. entries with mean $0$ and variance $1$.
We will designate the $k$-th task as the target.
Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
Concretely, we focus on the test error for the target task:
		\begin{align*}
			\te_k(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
		\end{align*}
%\end{itemize}

\todo{show that $\te_k(\hat{\beta}_t^{\TL})$ is less than both $\te_k(\hat{\beta}_t^{\MTL})$ and $\te_k(\hat{\beta}_t^{\STL})$.}

\textbf{The High-Dimensional Setting.}
%\todo{setup motivation and notations}
We would like to get insight on how covariate and model shifts affect the rate of transfer.
We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
This setting captures a wide range of applications of multi-task learning where we would like to use auxiliary task data to help train tasks with limited labeled data.
Furthermore, this setting is particularly suited to our study since there is need for adding more data to help learn the target task.

For the case of two tasks, we can get precise rates using random matrix theory.
For the sake of clarity, we call task 1 the source task and task 2 the target task,
i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.
We introduce the following notations for the high-dimensional setting
\[ c_{n_1} \define \frac{n_1}{p} \to c_1, \quad c_{n_2} \define \frac{n_2}p \to c_2, \quad \text{as } \ n_1, n_2\to \infty, \]
for some constants $c_1, c_2 \in (1,\infty)$.
A crucial quantity is what we call the \textit{covariate shift} matrix $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$.
Let $\lambda_1, \lambda_2, \dots, \lambda_p$ denote the singular values of $M$.
%

@@
